---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(keeper)
depot_delete("test")
```

# keeper

<!-- badges -->
[![R](https://img.shields.io/badge/language-R-blue)]()
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange)]()
<!-- badges -->

The goal of `keeper` is to provide a convenient way to store R objects or arbitrary files (plus additional notes) and retrieve them again later. 

To use the package, you need to know a few terms:

  * `box`: A container to store things. These things can be R objects or files.
  * `ìtem`: Anything that is stored inside the a `box`. 
  * `pack`: adding an item to a box.
  * `pick`: retrieving an item from a box.

Boxes are stored on your disk. Hence, anything put into it will remain there until you delete the box.
Technically, each box is a separate SQLite database. You can create as many boxes as you need.

## Usage

```{r example}
library(keeper)
depot_create("test")
depot_active()
depots()
depot()
keep("my_data", mtcars, "Data to keep for later")
depot()
df <- pick("my_data")
identical(df, mtcars)
```

## Installation

You can install the development version of keeper like so:

```r
# TBD
```

